Initial Analysis

### 2020-08-07 Scripts/Initial_Analysis.Rmd
All documents submitted to journal for revissions responses

SAU_Global_Data <-fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>%
  # Remove high seas and 207 and 208 that are unknown
  filter(!fishing_entity_id %in% c(213,223)) %>%  # 207,208
  # Allocate catch of islands to UK
  mutate(fishing_entity_id = ifelse(fishing_entity_id %in% c(219,220), 183,fishing_entity_id)) %>% 
  # Convert to 2019 real USD
  mutate(value = 1.16 * value) %>%
  # Average 10 years of data
  group_by(fishing_entity_id,taxon_key) %>% 
  summarise_at(c("catch","value"),
               mean,na.rm=T) %>% 
  gather("Variable","Value",catch:value)

@@

# Percentage species analyzed from the identified species
Total_spp_analyzed <-Total_SAU_Sampled$Sampled_nspp[1]/Total_SAU_id$id_nspp[1]*100 #63.23%

@@

# Read SAU non-reconstructed catch data from 2006 for comparrisonwith Sumaila
# Provided by Vicky Lam
SAU_FAO_Data <- fread(paste(my_path("D"),"Distribution/LVCatch_byYrEEZFETaxa_2005_09.csv", sep ="")) %>% 
  filter(#eezid != 0,
         year == 2006) %>%
  group_by(fishing_entity_id,taxon_key,eezid) %>% 
  summarise_at(c("sumcatch"),
               sum,na.rm=T)

@@

  # Get legend for cowplot
legend_plot <- get_legend(Catch_Plot)
# Re-plot without legend
Catch_Plot <- Catch_Plot +
  theme(legend.position = "")
  p<- ggdraw() +
  # Revenue circular
  draw_plot(Rev_Plot, x = 0, y = 0, width = 0.8, height = 1) +
  # Catch circular
  draw_plot(Catch_Plot, x = 0.4, y = 0, width =0.8, height = 1) +
  # Legend
  draw_plot(legend_plot, x = 0.2, y = 0.05, width = 0.59, height = 0.1) +
  # Labeks
  draw_plot_label(label = c("a", "b"),
                  size = 15,
                  x = c(0.1, 0.55),
                  y = c(1, 1)
  ) +
  # draw_plot_label(
  #   label = c("Revenue (Thousand USD) | Catch (Tons)","Per Km2"),
  #                 size = 6,
  #                 x = c(0.27,0.49),
  #                 y = c(0.66,0.63)
  # )
    draw_plot_label(
    label = c("Revenue     |     Catch",
              "(Thousand)  |     (Tons)",
              "(Per Km2)"),
                  size = 6,
                  x = c(0.41,
                        0.40,
                        0.48),
                  y = c(0.675,
                        0.65,
                        0.625)
  )

>>>>

# CPI in 2019/ CPI in 2010 × 2010  value = 2019  value

SAU_Global_Data <-fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>%
  # Remove high seas and 207 and 208 that are unknown
  filter(!fishing_entity_id %in% c(213,223)) %>%  # 207,208
  # Allocate catch of islands to UK
  mutate(fishing_entity_id = ifelse(fishing_entity_id %in% c(219,220), 183,fishing_entity_id)) %>% 
  # Convert to 2019 real USD
  mutate(values = 1.16 * value) %>%
  # Average 10 years of data
  group_by(fishing_entity_id,taxon_key) %>% 
  summarise_at(c("catch","value"),
               mean,na.rm=T) %>% 
  gather("Variable","Value",catch:value)

@@

# Percentage species analyzed from the identified species
936/length(unique(SAU_Global_Data$taxon_key))

Total_spp_analyzed <- Total_SAU_Sampled$Sampled_nspp[1]/Total_SAU_id$id_nspp[1]*100 #63.23%

@@

# Read SAU non-reconstructed catch data from 2006 for comparrisonwith Sumaila
# Provided by Vicky Lam
SAU_FAO_Data <- fread(paste(my_path("D"),"Distribution/LVCatch_byYrEEZFETaxa_2010_14.csv", sep ="")) %>% 
  filter(#eezid != 0,
         year == 2006) %>%
  group_by(fishing_entity_id,taxon_key,eezid) %>% 
  summarise_at(c("sumcatch"),
               sum,na.rm=T)

SAU_FAO_Data_a <- fread(paste(my_path("D"),"Distribution/LVCatch_byYrEEZFETaxa_2010_14.csv", sep =""))
SAU_FAO_Datab <- fread(paste(my_path("D"),"Distribution/LVCatch_byYrEEZFETaxa_2005_09.csv", sep =""))

# FAO data
total_FAO_catch <- bind_rows(SAU_FAO_Data_a,SAU_FAO_Datab) %>% 
  filter(eezid != 0) %>% 
  group_by(fishing_entity_id,taxon_key,eezid) %>% 
  summarise(mean_c = mean(sumcatch,na.rm=T)) %>% 
  group_by() %>% 
  summarise_at(vars(mean_c),sum)

total_sampled_FO_catch <- bind_rows(SAU_FAO_Data_a,SAU_FAO_Datab) %>% 
  filter(eezid != 0) %>% 
  filter(taxon_key %in% Species_Sampled$TaxonKey) %>% 
  group_by(fishing_entity_id,taxon_key,eezid) %>% 
  summarise(mean_c = mean(sumcatch,na.rm=T)) %>% 
  group_by() %>% 
  summarise_at(vars(mean_c),sum)

SAU_FAO_Data %>% 
  filter(taxon_key %in% Species_Sampled$TaxonKey) %>%
  group_by() %>% 
  summarise(sum(sumcatch))

@@

  # Get legend for cowplot
legend_plot <- get_legend(Catch_Plot)
# Re-plot without legend
Catch_Plot <- Catch_Plot +
  theme(legend.position = "")
  p<- ggdraw() +
  # Revenue circular
  draw_plot(Rev_Plot, x = 0, y = 0, width = 0.8, height = 1) +
  # Catch circular
  draw_plot(Catch_Plot, x = 0.4, y = 0, width =0.8, height = 1) +
  # Legend
  draw_plot(legend_plot, x = 0.2, y = 0.05, width = 0.59, height = 0.1) +
  # Labeks
  draw_plot_label(label = c("a", "b"),
                  size = 15,
                  x = c(0.1, 0.55),
                  y = c(1, 1)
  ) +
  # draw_plot_label(
  #   label = c("Revenue (Thousand USD) | Catch (Tons)","Per Km2"),
  #                 size = 6,
  #                 x = c(0.27,0.49),
  #                 y = c(0.66,0.63)
  # )
    draw_plot_label(
    label = c("Revenue     |     Catch",
              "(Thousand)  |    (Tonnes)",
              "  (Per km  )"),
                  size = 6,
                  x = c(0.41,
                        0.395,
                        0.48),
                  y = c(0.675,
                        0.65,
                        0.623)
  )
